---
title: "vignette"
output: html_document
---

Get and process climate data
```{r}
get_climate(source = "era5", r, tme, creds, out = "grid", rawout=NA, processout, file_prefix, clean = F)
```


Model vertical microclimates using GEDI data to derive information on the vertical distribution of plant area index.

Download GEDI data in a region of interest. As an example, we will use a 1km sqaure area in Mark Twain National Forest in Missouri, USA.

```{r}
pt = data.frame(lon = -91.08, lat = 37.69, region = "mark_twain_nf")
pt = vect(pt, geom = c("lon", "lat"), crs = "epsg:4326")
bbox = buffer(pt, 10)
e = ext(bbox)
```

Find gedi granules that cover the AOI.
```{r}
granules = gedi_finder(product = 'GEDI02_B.002', bbox = bbox)

```

Download GEDI data. gediDownload is from rGEDI package.
```{r}
gediDownload(unlist(granules)[1], outdir = "C:/Users/lsoif/Dropbox (UFL)/projects/tools/microclim3D/data/gedi_L2b/")

f = list.files("C:/Users/lsoif/Dropbox (UFL)/projects/tools/microclim3D/data/gedi_L2b/", pattern = ".h5", full.name = T)
gedi = readLevel2B(f)
#gedi = getLevel2BVPM(gedi, c("pgap_theta"))

level2b = gedi@h5
groups_id<-grep("BEAM\\d{4}$",gsub("/","",
                                     hdf5r::list.groups(level2b, recursive = F)), value = T)

  m.dt<-data.table::data.table()
  pb <- utils::txtProgressBar(min = 0, max = length(groups_id), style = 3)
  i.s=0
  for ( i in groups_id){
    i.s<-i.s+1
    utils::setTxtProgressBar(pb, i.s)
    level2b_i<-level2b[[i]]
    m<-data.table::data.table(
      beam<-rep(i,length(level2b_i[["shot_number"]][])),
      shot_number=level2b_i[["shot_number"]][],
      algorithmrun_flag=level2b_i[["algorithmrun_flag"]][],
      l2b_quality_flag=level2b_i[["l2b_quality_flag"]][],
      delta_time=level2b_i[["geolocation/delta_time"]][],
      lat_lowestmode=level2b_i[["geolocation/lat_lowestmode"]][],
      lon_lowestmode=level2b_i[["geolocation/lon_lowestmode"]][],
      elev_highestreturn=level2b_i[["geolocation/elev_highestreturn"]][],
      elev_lowestmode=level2b_i[["geolocation/elev_lowestmode"]][],
      height_lastbin=level2b_i[["geolocation/height_lastbin"]][],
      height_bin0=level2b_i[["geolocation/height_bin0"]][],
      pai_z=t(level2b_i[["pai_z"]][,1:level2b_i[["pai_z"]]$dims[2]]),
      pgap_theta_z = level2b_i[["rv"]]$dims t(level2b_i[["pgap_theta_z"]][,1:level2b_i[["pgap_theta_z"]]$dims[2]]))
    m.dt<-rbind(m.dt,m)
  }
  colnames(m.dt)<-c("beam","shot_number","algorithmrun_flag",
                    "l2b_quality_flag","delta_time","lat_lowestmode",
                    "lon_lowestmode","elev_highestreturn",
                    "elev_lowestmode","height_lastbin",
                    "height_bin0",paste0("pai_z",seq(0,30*5,5)[-31],"_",seq(5,30*5,5),"m"))
  close(pb)

 for (i in groups_id){
    i.s<-i.s+1
    utils::setTxtProgressBar(pb, i.s)
    level2b_i<-level2b[[i]]
    m<-data.table::data.table()
    #col = cols[1]
    for (col in cols) {
      h5.address = var.map[[col]]
      if (is.null(h5.address)) {
        if (col %in% names(level2b_i)) {
          h5.address = col
        } else {
          if (i.s == 1) warning(sprintf("The column '%s' is not available in the GEDI2B product for BEAM %s!", col, i))
          next
        }
      }
      m[,eval(col):=level2b_i[[h5.address]][]]
    }
    m.dt<-rbind(m.dt,m)
  }


level2b_i[[i]]

```

